---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kclique

<!-- badges: start -->
<!-- badges: end -->

The goal of kclique is to enumerate all maximal kcliques within a k-partite graph.

## Installation

You can install the development version of kclique from [GitHub](https://github.com/) with:

```{r install package, eval = FALSE}
# install.packages("devtools")
devtools::install_github("RemiMahmoud/kclique")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE, warning=FALSE}
library(kclique)
```



### Load toy data

```{r}

data("data_example", package ="kclique")

knitr::kable(head(data_example))
```

As an example, imagine a set of three factors, with various modalities and combinations of modalities. You can represent the co-occurence of the modalities by a graph.


### Set graph

```{r}
# get graph from the data
graph_example <- get_graph_from_dat(data_example)
```

### Plot data

We can plot the graph, using one color for each factor
```{r}
plot_graph_example <- plot_graph(G = graph_example, dat = data_example)
plot_graph_example
```


### List maximal kcliques

If we want to look for all the maximal complete factorial design, we need to enumerate all the maximal kcliques present in the graph.

```{r}
kcliques_example <- kclique::maximal_kclique_enumeration(graph_example, data_example)

knitr::kable(kcliques_example,col.names = "List of kcliques")
```

### Format kclique in a nice output format



```{r}
tibble_kclique <- function_list_kcliques_to_tibble(kcliques_example, data_example)

knitr::kable(tibble_kclique)

```

We identified 9 maximal kcliques, involving various combinations of factors' modalities.

### Highlight a kclique



```{r}
plot_kclique_1 <- plot_kclique(G = graph_example, dataset = data_example, tibble_kcliques = tibble_kclique, vector_kcliques = 1)
plot_kclique_1

plot_kclique_3 <- plot_kclique(G = graph_example, dataset = data_example, tibble_kcliques = tibble_kclique, vector_kcliques = 3)
plot_kclique_3
# plot_graph_example

```



<!-- We identified 9 maximal kcliques, involving various combinations of factors' modalities. -->





```{r cars, echo = FALSE}
# summary(cars)
```

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>. -->

<!-- You can also embed plots, for example: -->

```{r pressure, echo = FALSE}
# plot(pressure)
```

<!-- In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN. -->
