---
title: "How-to-use-kclique"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How-to-use-kclique}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

library(kclique)
library(dplyr)
        
library(igraph)
library(tidygraph)
```


# Load toy data

```{r}

data("data_example", package ="kclique")

knitr::kable(head(data_example))
```

As an example, imagine a set of three factors, with various modalities and combinations of modalities. You can represent the co-occurence of the modalities by a graph.


# Set graph

```{r}
graph_example <- get_graph_from_dat(data_example)
```

# Plot data

We can plot the graph, using one color for each factor
```{r}
plot_graph_example <- plot_graph(G = graph_example, dat = data_example)
plot_graph_example
```


# List maximal kcliques

If we want to look for all the maximal complete factorial design, we need to enumerate all the maximal kcliques present in the graph.

```{r}
kcliques_example <- kclique::maximal_kclique_enumeration(graph_example, data_example)

knitr::kable(kcliques_example)
```

# Format kclique in a nice output format

## Wide format

```{r}
tibble_kclique <- function_list_kcliques_to_tibble(kcliques_example, data_example)

knitr::kable(tibble_kclique)

```

We identified 9 maximal kcliques, involving various combinations of factors' modalities.

## Long format

We can also have a long format for the tibble

```{r}
tibble_kclique <- function_list_kcliques_to_tibble(kcliques_example, data_example, format = "long")

knitr::kable(head(tibble_kclique))

```





